---
title: "EV Power - Lab 4 Project Report"
format: typst
---

# Example Solution 1

## **Part 0: libraries**

```{r}

```

## **Part 1:** **Defining Research Question**

Chosen Question: Which states has the largest increase of shared renewable energy from 2021-2023? Do states with higher EV registrations sourcing a greater proportion of electricity from renewable energy? Is there a correlation between a state's average energy price and its renewable energy usage? If so, describe this trend. Is there an emergence of states where both renewable energy share and EV registrations are rapidly increasing?

Question used for mapping:
"Is there a correlation between a state's average energy price and its renewable energy usage? If so, describe this trend."
*NOTE* will be only using 2023 data for mapping
```{r}
ru_2021 <- read_csv("data/renew-use-2021.csv")
ru_2022 <- read_csv("data/renew-use-2022.csv")
ru_2023 <- read_csv("data/renew-use-2023.csv")
tu_2021 <- read_csv("data/total-use-2021.csv")
tu_2022 <- read_csv("data/total-use-2022.csv")
tu_2023 <- read_csv("data/total-use-2023.csv")
EVR <- read_csv("data/ev-registrations-by-state-2023.csv")
AVEP <- read_csv("data/av-energy-price-2021-2023.csv")
```

```{r}
 AVEP_joined <- us_states |>
    left_join(AVEP, by = c("name" = "Total energy average price, dollars per million Btu,,,"))

ggplot(AVEP_joined) +
    geom_sf(aes(fill = "Total energy average price, dollars per million Btu,,,"), color = "white") +
    scale_fill_continuous(name = "Dollars per Million Btu", na.value = "grey90") +
    labs(title = "US States by Average Energy Price") +
    coord_sf(xlim = c(-125, -66), ylim = c(24, 50), expand = FALSE)+
    theme_minimal()
# Code does not work, too many errors 
```

## **Part 2: Data Preparation and Cleaning**

```{r}

```

## **Part 3: Joining / Pivoting Datasets for Analysis**

```{r}

```

## **Part 4: Mapping Visualization**

```{r}

```